Untitled

### 2020-05-27 algo_rank_harmony.Rmd
added choosing_harmony document

```{r}
library(readr)
smart_normal <- read_rds("data/smart_harmony_norm.rds") %>% mutate(rank_normal = row_number())
```

@@

data_unite %>% select(-c(MMPD_normal, MMPD_gamma, MMPD_weibull, MMPD_general))
data_unite %>% select(-c(rank_normal, rank_gamma, rank_weibull, rank_general))

```

@@

## Distances follow Weibull
```{r}
read_rds("data/ smart_cric_weibull.rds")%>% knitr::kable()
```

@@

```{r}
library(readr)
read_rds("data/ smart_cric_gamma.rds") %>% knitr::kable()
```

## Distances follow Normal 
```{r}
read_rds("data/ smart_cric_normal.rds")%>% knitr::kable()
```

## Distances follow general 
```{r}
read_rds("data/ smart_cric_general.rds")%>% knitr::kable()
```

>>>>

```{r}
library(readr)
smart_normal <- read_rds("data/smart_harmony_norm.rds") %>% mutate(rank_normal = row_number())

library(readr)
smart_chi <-read_rds("data/smart_harmony_chisq.rds") %>% mutate(rank_chi = row_number())
```

@@

data_unite <- smart_chi %>% 
  left_join(smart_weibull, by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
   rename("MMPD_chisq" = "mean_max_variation.x", "MMPD_weibull" = "mean_max_variation.y") %>% 
    left_join(smart_gamma,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>%  
  rename("MMPD_gamma" = "mean_max_variation") %>% 
  left_join(smart_normal,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("MMPD_normal" = "mean_max_variation") %>% 
   left_join(smart_general,  by = c("facet_variable", "x_variable", "facet_levels", "x_levels")) %>% 
  rename("MMPD_general" = "mean_max_variation") %>%  select(-c(facet_levels, x_levels))

data_unite %>% select(-c(MMPD_normal, MMPD_gamma, MMPD_weibull, MMPD_general, -MMPD_chisq)) %>% knitr::kable()
data_unite %>% select(-c(rank_normal, rank_gamma, rank_weibull, rank_general, rank_chi)) %>% knitr::kable()
```

@@

## Distances follow Weibull
```{r}
cric_weibull <- read_rds("data/ smart_cric_weibull.rds")%>% mutate(rank_weibull = row_number())
```

@@

```{r}
library(readr)
cric_gamma <-read_rds("data/ smart_cric_gamma.rds") %>% mutate(rank_gamma = row_number())
```

## Distances follow Normal 
```{r}
cric_normal <-read_rds("data/ smart_cric_normal.rds")%>% mutate(rank_normal = row_number())
```

## Distances follow general 
```{r}
cric_general <- read_rds("data/ smart_cric_general.rds")%>% mutate(rank_general = row_number())

data_unite %>% select(-c(MMPD_normal, MMPD_gamma, MMPD_weibull, MMPD_general))
data_unite %>% select(-c(rank_normal, rank_gamma, rank_weibull, rank_general))
```

### 2020-05-27 algo_validation.Rmd
added choosing_harmony document

```{r}
cricket_data <- read_rds("data/cricket_data.rds")
cricket_data %>% hist_distance(gran1 = "lag_field", gran2 = "over", response = "runs_per_over", hierarchy_tbl = hierarchy_model)
```

@@

@@

>>>>

@@

# cricket_data %>% histogram_distance(gran1 = "over", gran2 = "inning_match", response = "runs_per_over", hierarchy_tbl = hierarchy_model)
```

```{r}
cricket_data <- read_rds("data/cricket_data.rds")

@@

```{r, eval = FALSE}
sm <- smart_meter10 %>%
  filter(customer_id %in% c(10017936))
 .data = sm
 response  = "general_supply_kwh"
 .data %>% hist_distance(gran1 = "hour_day", gran2 = "wknd_wday", response = "general_supply_kwh")
```
